
\subsection{Introduction}

uk legal stuff
+ sector regulator
  + market review under sector powers
  + ex ante controls and rules
+ concurrent powers
  + market study EA 2002
  + market investigation reference (MIR) to CMA
  + CA98 enforcement
+ CMA powers
  + Merger control
  + Market investigation
  + Cartel prosecution
+ enterprise and regulatory reform act 2013 affects concurrency
+ sectors with own legislation
  + CAA
  + FCA
  + Ofgem
  + Ofcom
  + ORR
  + PSR
  + NI
  + Ofwat


UK
	Ofcom	Communications Act 2003		Postal Services Act 2011
	Ofgem	Gas Act 1986		Electricity Act 1989
	Ofwat	Water Industry Act 1991
	ORR	Railways Act 1993		Railways and Transport Safety Act 2003
	NIAUR	Electricity (Northern Ireland) Order 1992		Gas (Northern Ireland) Order 1996
	CMA
	PSR	Financial Services (Banking Reform) Act 2013
	FCA	Financial Services and Markets Act 2000
	CAT
	NHS England	Health and Social Care Act 2012

	EA 2002
		set up OFT and CAT

		allows market investigations

		sets up phase 1 and phase 2 merger investigations
			does a merger result in substantial lessening of competition

		have concurrent powers with sector regulators
	CA98
		chapter 1
			prohibits agreements by effect or object

		chapter 2
			prohibits abuse of dominance
		have concurrent powers with sector regulators
	EU
		Digital Markets Act 2022
		Artificial Intelligence Act 2024

	MIFID 2
		including fca reporting requirements

	Article 26 of MiFIR?
	European Market Infrastructure Regulation (EMIR)
		also requires FCA reporting?
	FCA
		FCA handbook
			SUP
				Contains rules on product sales data reporting

Payment systems directive/regulations and equiv UK onboarding
UK onboarding of legislation more generally


restrictions by object, by effect for competition

immunity for whistleblowing

early settlement

rules against price increases.

fair pricing, excessive pricing

CBA
ex ante analysis?
ex post analysis?
theories of harm
\subsection{europe pre EU}
anti trust stuff brought by allies at end of ww2. to break up political power.
\subsection{EU: 1951 treaty of paris}
european coal and steel community (ECC)
prevents barriers and discriminatory access

article 65 bans agreements and concerted practices which directly or indirectly which prevent, restrict, distory competition
+ basis of article 81 of rome, 101 of lisbon

article 66(7) on abuse of dominance
+ basis of 82 of trome, 102 of lisbon

high authority is governing body

66 on mergers, had to be approved by high authority
\subsection{EU: 1957: treaty of rome}
aka treaty establishing the european economic community
created the eurpean economic community

mergers not in scope
article 81 on practices, went on to be 101
article 82 on dominance
went on to be 102
\subsection{EU: 1992: Maastricht treaty}
amends rome?
\subsection{EU: 2007: Lisbon treaty}
aka treaty on the functing of the european union (TFEU)
amends maastricht
includes 101 (prev 81)
+ for cartels
includes 102?
+ for market dominance
\subsection{other UK legislation (how does this interact with EU legislation?)}

Competition Act 1998 (CA98)
Can investigate and enforce breach of this.

Financial Services and Markets Act 2000 (FSMA)
Can investigate a regulated market to see if competition is working well?
Can carry out market study
Can make Market Investigation Reference (MIR) to CMA.
Concurrent with CMA

Enterprise Act 2002
Act investigate a market? Broader option of markets than FSMA


\subsection{market investigation}

