
\subsection{Introduction}

Private International Cartels Full Data 2019 edition
+ https://purr.purdue.edu/publications/2732/2

econ
	difference between collussion and cartels
	+ legal diff, game theory diff

one monopoly price theorem


ramsey pricing here

maybe an h3 on power and taxation
+ lipsey and lancaster
+ diamond mirlees


split out page on structural reduced.
+ page on strucural reduced
+ page on estimated market demand elasticity (ie no power, monopsony)
  * could also do estimating supply elastiicty. assumptions are similar, perfect competition
+ estimate firm own price elasticity. has to be in IO
  * firms set price according to maximising, so if we know the markup, we know elasticity
\subsection{h3 monopoly pricing}
\subsection{h3 horizontal homogenous}

price agreements and game theory
+ game theory with price agreements in contract
+ game theory without price agreements in contract

welfare impact. consumer surplus vs consumer + producer surplus

explicit page on mergers. increase prices, but other models for efficiency.

modelling firm behavour, how much to produce

Measuring market power using market entry

price matching

modelling entry
entry: 2 stage game. decide to enter, then decide to compete.
2 games. already incumbants, or no.

merger simulation on horizontal homogeneous
+ Counterfactual to merger: firm could fail, worse for market than merger
+ Merger simulation: comparative statics; structural models

Estimating markup: market share plus demand elasticity

\subsection{h3 horizontal multi good}

price dispersion. metric

defining market with
+ Full Equilibrium Relevant Market (FERM). Alternative to SSNIP.
SSNIP
celophane fallacy? by definition already profit maximising

Definition: contestable market

Can define markets more ad-hoc: eg travel to heathrow market, can use travel times to define

Market definition: geographic, product substitution

monopolistic competition

\subsubsection{barriers to switching otherwise homogeneous goods and pricing renewing customers}
\subsubsection{producers of multiple homogeneous goods and bundling? does this require monopoly and so doesn't fit here?}

bundling:
+ grand bundling
+ mixed bundling (sell separately with discount for both.)
always more profitable, better for consumers too

pure bundling: only sell bundling.
\subsection{h3 monopsony}
start with monopsony. show competitive is limit
\subsection{h3 vertical}
retail price maintenance
vertical integration
+ margin squeeze
+ forclosure
double margin
exclusive dealing

pass through.

most favoured nation wide
most favoured nation narrow

merger simulation in vertical
\subsection{h3 networks}
networks:
+ benefit goes up as users go up
+ could also have negative effects - congestion

competition between networks
+ multihoming
+ winner takes all - implications for investment

h3 on two sided markets
+ pricing

