
\subsection{Introduction}


2 player game: nine men's morris
1 player: sliding game.
solitaire?
rubik's cube

Reinforcement learning: aixi. Application of solomonoff?

puzzles:
+ rubic
+ wordle
+ tower of hanoi

goal agents v util agents. just find solution v find best solution

reinforcement learning split out:
+ q learning
+ temporal difference learning
\subsection{Big h3: Decision theory under certainty}
\subsubsection{Certainty}
for decision theory tree search: can need to find solution (ie pay off is 1 or 0) or "best" solution. if there are time/memory constraints, may not want to wait for best. may not know what best is until fully exhausted
\subsection{Big h3: Intertemportal decision theory under certainty}
\subsection{Big h3: Decision theory under known uncertainty}
\subsection{Big h3: Decision theory under unknown uncertainty}
\subsection{Big h3: Game theory under certainty}
\subsection{sequential}
divide dollar
Ultimatum game
\subsubsection{simulataenous games}
keysian beauty contest
+ Prisoner's dilemam
\subsubsection{deep sequential}
forward pruning (only look at best moves)

tables for start and end game eg in chess
\subsection{Big h3: Game theory under uncertainty}
in game theory, note that it is not stationary, so different to MDP and POMDP
\subsection{Big h3: Robotics}
\subsubsection{SAT planning}
planning graph

section on scheduling

critial path, critical path method
\subsubsection{nlp}
textual entailment in NLP.

Does one statement imply another, negate another, irrelavent to another?

task: assessing textual entailment

assessing semantic similarity

sentiment analysis

machine translation

