
\subsection{Introduction}

Database join. Shuffling. Broadcast join. Sorted bucket join

dbt in name for sql big page
sql: on-line transaction processing (OLTP); on-line analytical processing (OLAP)
"databases and ELT/ETL"

gnu recutils. text based database

Redis

shift thing on sql. take lagged variable

COMMIT statement in SQL

page on SQLite
page on postgresql

data build tool ()
sql: add primary keys; multiple primary keys
sql: common table expression (CTE)
sql: normalisation and normal forms. first normal form. can't use row order. can't have differnt data types in column (can't do this anyway in sql). have to use a primary key. prevent multiple rows with the same primary key.

2nd normal form. storing repeated data across rows rather than using separate table. eg if table has transactions, have just the customer ID rather than eg name, age as well.
also in 2nd: deletion anomoly. insertion anomoly.

sql: creating and saving new tables based on others.

in sql page on time series and panel data (windows)

dynamic sql

databases
+ why if you don't need multiple systems?
+ first, multiple users on 1 system
+ multiple processes on same data
+ use of library for read write stuff. makes coding simplier
+ faster access than eg read/write csv

database:
w own h3 or big page?
manage multiple attempts to read change data
ensure data structure maintained
acid acronym in databases
need guaranteed write ownership, accuracy

serialised data:
+ related but different: csv, yaml json etc
\subsection{data strategies}
Data warehouse
Data warehouses (structured). Datalakes (not structured)
Data cloud
Data lake

REST? REpresentational State Transfer

Extract, transform, load(ETL)
+ older. get data (extract) transform (clean,) load(save somewhere visible)

Extract, load, transform(ELT)
+ data originally stored uncleared, unstructured. processed within data structure from there
+ essentially means do the transformation (ie cleaning) within sql, nosql, or whatever

