
\subsection{Introduction}

have thing on various graphics there. cga, ega, vga, svga. are hardware oututs

page on flash. flasharch program to run flash files?

xdg-open (opens in desktop environment. eg run "xdg-open file.jpg" to open in default image viewer)
fonts in 2d
TrueType fonts (ttf)
OpenType font (otf)

linux: imagemagick

2d: alpha compositing (transparency stuff)


on graphics, page for each of prominant ppu
+ nes
+ gb/gbc
+ gba
+ snes
+ genesis
+ master system/gg
+ arcade: CPS Super Chip

GNU texinfo


GNU roff (groff)
mobi
epub

page on replacing login shell (they don't use one? do different approach?)

graphics/audio firmware?

gnu plotutils (graphics)

Mathematical Markup Language (mathml)

gimp

\subsection{2D}
scalable vector graphics (SVG)

Computer engineering frame buffer

decompilation of stuff with images:
+ can open as images to find uncompresed images

big page on graphics
+ framebuffer

+ bitmap on 2d
+ vector based on 2d
+ image compression h3
  * jpeg

+ colours
  * rgb model
    1. \#ffffff (6)
    2. \#fff(3)
  * indexed color
    * eg option of 7 colors and 8th for transparency. 7 colours defined in palette
    * allows sprites to take up less space, be easier to process, to integrate transparency

tile maps for eg nes backgrounds
separate to sprites
can enable scrolling in 1 direction at least?
can say mirror/flip
bigger than screen. can update tile map by changing when offscreen

animated tilemaps?
relation between rom and ram for tilset? uncompress when bring out tiles?

2d graphics: masks. bitmaps.
\subsection{2d hardware on consoles}
on eg snes/genesis, multiple tilemaps? transparency?

\subsection{dos (CGA, EGA, VGA)}
CGA (color graphics adapter)
EGA (enhanced grahics adapter)
VGA (video graphics array)
\subsection{nes}
nes graphics:
+ tiles of 8x8.
+ two layers. background. sprites
+ 4 colour limit on tiles

\subsection{snes}
snes:
+ tiles of 8x8 or 16x16
+ up to 4 background layer
+ smoother scrolling of background layers
+ modes 0-6 for different setups of scrolling layer, bits per pixel in layers
+ between 2 and 8 bits per pixel for colours (between 4 colours and 256)

\subsection{markup and latex}
latex: new line for each sentence
allows picked up by diff etc easier

h3 markup language
+ html
  * pug
+ markdown
+ epub
+ org mode
+ pdf
+ css
+ latex
+ PostScript
+ djvu

Utf8 ASCII etc. More complex on post c?
\subsection{2d physics}

2d physics.
+ colission detection. hurtbox/hitboxs

\subsection{desktop and window environments}
+ wayland?

in graphical deskptop environment, something on polkit? allows authentication outside the non graphical terminal? or is this just an arch thing.

pages on desktop environments:
+ KDE
+ GNOME
+ Xfce
+ LXDE
+ Cinnamon

xorg
+ /usr/share/X11/xorg.conf.d/
+ /etc/X11/xorg.conf.d/
+ /etc/X11/xorg.conf OR /etc/xorg.conf
+ can generate conf template using Xorg :0 -configure

tiling window managers
gtk
qt
\subsection{video and ffmpeg}
+ video codec
  * encorder page, then page on container?
  * h.263
  * mpeg 2
    1. h.262/mpeg-2 part 2
  * mpeg 4
    * mpeg-4 part 2
    * advanced video coding
    * h.264 or mpeg-4 part 10
  * mpeg-h
    * high efficiency video coding (hevc)
    * h.265
  * vp8 (open)
  * vp9 (open)
  * av1 (open)
  * concept of profiles
  * concept of levels
  * average bitrate
  * two-pass
  * 1 pass
  * constant quality
  * constrained quality
  * constant quality
  * lossess

video compression. containers. formats. bitrates. audio formats etc


