
\subsection{Introduction}

python data: engineering pipelines using apache airflow (python specific)





more packages related to pandas
pandera
dask
modin
PySpark dataframe
vaex

\subsection{pytorch}
pytorch: transfomer; lstm; convolution
pytorch stuff
pytorch.nn.Sequential (stack layers together)
nn.Linear(a,b)
nn.ReLU()
nn.Sigmoid()

nn.Module() (class, can inherit from it, has methods)

torch.optim
torch.optim.Adam()

can define loss functions
nn.BCELoss (binary cross entropy)
\subsection{numpy}
arr.np.array([1,2,3])
can create views and copies
x = arr.view()
y = arr.copy()
chaning x changes arr, changing y doesn't change arr

can check with x.base, y.base, arr.base
returns none if not a view

note that no () at end.

numpy: difference between view and copy
numpy data types. NaN only float, not int? does numpy support int?
\subsection{pandas}
 can do the base copy view checks for can do for series too, as in numpy
data types in pandas, inc objects

concepts of missing data in pandas. different approaches, what role None and NaN play, also NaT, NASA
shift on pandas

page on pandas:
+ loc, iloc, selection with brackets, at, iat (at and iat are for elecemnts, loc and iloc for sub df). loc and at work on named index, iat and iloc on index offset? is that right?.
df.\_is\_copy
df.\_is\_view
\subsection{Non data packages (maybe separate big page? something else?)}
h3 on econ modules?
+ quantecon
+ dynare
\subsection{specific non standard library packages}

pystan in python

page on mpmath (arbitrarily accurate numbers)

page on sympy (depends on mpmath)


