
\subsection{Introduction}

RGB, scart
S video
Composite
Component
Vga

Twisted nematic screen TN
In plane switching ips screens

electronics: crystal radio

engineering
	electromagnets

Residual circuit breaker

Electronics: logic analyser

Verilog in electronics? It's a language, but is useful even without software? Alt can have big page on domain specific languages and packages
+ also vhdl (vhsic hardware description language), (very high speed integrated circuit)

Electronics: printed circuit board; wire wrap; point to point construction
Electronics busbar

ram: 2 types: static random-access memory (SRAM); dynamic random access memory (DRAM)
electical stuff: field-effect transistor; bipolar junction transistor; point contact transistor;
transistor-transistor logic; diode-transistory logic; resistor transistor logic

truth table. col for each variable. column for outcome.
karnough map. on 2 plane. eg combine ab and have against c. cells filled with results.
eg if 3 var can have 4x2 table. each ab comb on one axis, c on other.
can then look at the map and group the 1s in powers of 2, ie 1 2 4 etc
can then turn this into logical circuit. ie can take any truth table and make digital signal versions.
"OR" a bunch of "AND"s. each group of 1s is an AND, then all separate groups are put into OR. how to know which way to orient k map? trial error?

BIg page on electrical engineering
composite video
rgb video
scart?
component video
surface acoustic wave (SAW) on electronics

electronics: making each type of logic gate with transistors, diodes

integrated circuits: 555 timer

flip flop in electronics


electronics: making each type of logic gate with transistors, diodes

electronic: integrated circtuits

l1, l2 and l3 cache

page on memory controller, for accessing external memory

Clocks of CPU
+ what does it mean for clock speed of cpu to be different to ram?

computer inputs engineering:
+ keyboard
+ mouse

\subsection{motherboard types}

case/motherboard sizes:
+ EATX (Extended ATX)
+ ATX (Advanced Technology eXtended)
+ MicroATX
+ Mini-ITX

\subsection{BASICS}

\subsection{batteries, wires and resistors}

\subsection{circuit diagrams and parallel and sequential circuits}

\subsection{switches and variable resistors}

\subsection{diodes and capacitors}

diode
capacitor

\subsection{INPUT AND OUTPUTS}

\subsection{light outputs and solar panels}

cathode ray tube
LED tv
LCD tv
Plasma tv
\subsection{motor input and output}

\subsection{microphone and speaker}

+ sound fonts
+ Audio sythesiser. Midi?

\subsection{radio}

picking up radio signal
giving out radio signals


radio:
+ am fm ssb
+ receiver vs transmitter vs transeiveer
+ frequency ranges. hf, vhf, uhf
+ channels

\subsection{temperature and moisture sensors}

+ more: temperature sensor; moisture sensor

\subsection{digital and analogue clocks}

electric "analgoue" clocks
electric digital clocks

\subsection{INTERMEDIATE}

\subsection{circuit boards}

discrete circuits
printed circuit boards (PCBs). aka printed wiring boards (PWBs)

"bread boards"?

printing circuits and washing them to make conduct

soldering wires to circuit

discrete circuits

parallel and sequential circuits

\subsection{ground and mains}

role of ground (does this only make sense in context of mains ie no battery?)

\subsection{LOGIC}

\subsection{implementing an adder, and other logic stuff inc nand gates, or gates, etc}

various logic gates from transistors

implementing logic with just an adder?
+ "or". multiplying together whether = 0?
+ "not" from arrangement of jump?
+ "and" from arrangement?

\subsection{more complex}


Programmable logic device

\subsection{INTEGRATED}

\subsection{integrated circuits}

integrated circuit design:
+ Floorplan

semi conductor

integrated circuits

integrated circuits: uses semi conductors and photolithography
integrated circuits still embedded within discrete circuits (eg cpu in motherboard)

555 timer

types
+ large scale integration (LSI)
+ very large scale integration (VLSI)

\subsection{Electronic design automation}


\subsection{fpga}

page on field-programmable gate array (in advanced)
+ logic block or configurable logic block (CLB)

\subsection{ram and hard storage}

Programmable ROM

volatile memory
non-volatile memory


FRAM as type of memory

memory:
+ EPROM
+ EEPROM

punchcards

memory page
memory banking
ecc on ram
ddr12345

storage:
+ cd/dvd/bluray
+ tapes
+ Punch card

storage:
+ Input/Output operations per second (IOPS)

Random-Access Memory (RAM)

Read/write times do not depend on location of data. They do if some other types?

ecc
+ or is this later? requires more advanced system?

ram is example of device. can be  read or written to.

hard drives:
+ smr vs cmr
+ solid state drives

\subsection{digital camera}

these use semiconductors


