
\subsection{Introduction}

what are the linux C extensions? discuss in big page in same context as hosted C? Does musl include Linux c extensions?

fuzz testing
+ C linux has an h3 on static analysis, dynamic analysis and gdb. Maybe this could be its own separate big page along with development stuff?
+ could be in "More on linux, after IDEs"
+ or could move/adapt "validating code and compilers"


gnu autoupdate/autoconf?

"..hosted C AND BOOTSTRAPPING ASSEMBLERS AND A C COMPILER"

ldd command. shows what libraries associated with command. owned by glibc


ensure not missing any from gnu/unix:
https://en.wikipedia.org/wiki/C\_POSIX\_library

using backtrace() function from glibc to do stack trace

shared object: .so.n (n is version number in integer. eg v 6.0 through 6.9 would have same interface so could be used in .so.6)
static library: .o


difference between GAC (GNU assembly code) and NASM somewhere

\subsection{COMPILING}
printk (print in kernel world, different to printf in user world)
module\_init() and module\_exit() to specify functions to run when module loaded and unloaded
\begin{verbatim}

#include <linux/module.h> to use module_init() and module_exit()
#include <linux/init.h> to use __init and __exit
#include <linux/fs.h> to use file_operations struct
\end{verbatim}

\subsection{C POSIX library (eg <sys/mman.h>}
c standard library allows for editing environment variables

mmap and mummap different to heap? used for accessing files and devices
+ is this standard library or something else?

\subsection{c standard library}


heap stuff
+ c sytstem calls used to allocate heap. why?
+ mmap munmap vs malloc
+ rather than allocate for each part of the heap, can allocate huge amount and then allocate within by hand. allows domain specific understanding to be reflected. can increase efficiency.

error handling

+ c printing: %d; %x, %o, (%X is hex but in caps eg 0xFFFF vs 0xffff)

linkers. static. dynamic.
c exception handling
+ raise requires signal.h

use of static in c, in unix (applies to other files, not really core c logic) (is is part of library)?

for unix: grab c arguments using main
int main (int argc, char **argv)

DNDEBUG can use this flag to remove asserts. used for production
<fenv.h> floating point functions for controlling specific work environment?

following 2 are macros for int and float respectively. seem to be environemnt/distro related?
<limits.h>
<float.h>

<iso646.h> macros so can say "and" instead of \&\&. here not in c because based on macros
<stdnoreturn.h> macros on returning?
<stdalign.h> macros for "alignment"???
\subsection{alternatives to glibc: musl; bionic; newlib}
\subsection{--NEW LAYOUT--}
\subsection{GNU Binutils}
assembler: assemvly to object file
linker: object file to executable
eg object has placeholders for how to implement printf. linker gets this from libraries. relocation
\subsection{GCC and make}
use of \$(MAKE) in makefiles.
up-clean:
  \$(MAKE) down-clean
  \$(MAKE) up

when compile in gcc, specify the example.c file to be compiled too
make
+ installing
+ configure (get info on system for make process)
+ make (compile)
+ make install (copy files to system)

gcc:
+ -S flag compiles to assembly
+ -c flag creates object file
+ -ffreestanding to do that over hosted
+ -fhosted to force hosted
\subsection{stdlib.h}

\subsection{rest of standard library}

limits and float on same page? also stdint?
\subsection{alternatives to glibc}
\subsection{scientific libraries}
c headers on stuff:
+ GNU scientific library. GSL.
+ Basic Linear Algebra Subprograms (BLAS) (is this just cpu?)
+ openmp (open multiprocessing) (is this cpu header for c?)
\subsection{linux specific headers}
outside of standard library is also some linux/posix specific header stuff
+ fcntl.h
+ unist.h
note, these are not part of c standard library
\subsection{tools for making stuff}
m4 (macro processor)
autoconf
automake
debugedit
libtool
\subsection{Analysing programs}
page on linter
\subsection{make own c library}
making own header file
\begin{verbatim}
#include "myhead.h"
\end{verbatim}


best practice: splitting up function declearation and function definitions
just have declarations in .h
make .c file with same name. eg example.h and example.c
have definitions in c
\begin{verbatim}
#include "example.h" in example.c
\end{verbatim}


can guard against name already existing in .h file
\begin{verbatim}
#ifndef MY_HEADER_H
# define MY_HEADER_H
//put your function headers here

#endif
\end{verbatim}

\subsection{compiling the linux kernel}
Dynamic Kernel Module Support (DKMS)
+ Allows modules with source code outside linux kernel source tree

page on kthreads.h

h3 on changing linux kernel
+ compiling the kernel
+ flags
+ adding/removing modules
+ pattching code
+ eBPF (extended berkely packet filter, but not really a network thing. allows programs to run skipping the kernel??)

