
\subsection{Introduction}


union in c

similar syntact to a struct, but only memory of largest element allocated. that means variables overlap. can use to do automatic type conversion, pseduo polymorphism. eg can have large int and 
struct of chars in a union. each char represents a part of the large int. can use to model eg a register.

freestanding c doesn't have to start at main? confirm
H3 in c: type systems and type safety and static type checking

c: how to do long or float when ALU doesn't support (eg 32 bit on 16 bit CPU, float on int only ALU)

c:
+ on c, thing on what c does if fpu, int mul, int division not available. which algorithms does it use. same for powers? also thing for int division, remainder.
+ power not in c, need math.h
+ how it checks for greater than, equals?

thing on implementing the assembly algorithms discussed in various pre C parts
+ Array algorithms
+ Integer algorithms

does C have any built in array operations, eg insert, pop?

can do complex numbers with \_Complex? complex.h in hosted expands on this, but \_Complex available in base C?

static: two uses. inside function means keeps value between calls. static global variable is only seen in file made in

does freestanding need main? does it use main? \_\_name\_\_== "Main" or whatever?
if not then that stuff should be moved to GNU/Linux

if (var) evaluates to true if var is a positive integer

\subsection{h3 c unstructured (int)}

?? below. what are the list of storage classes? is typedef an storage class? seems like something to make it safer to write functions. similar for extern

c storage classes. all variables/functions are one of these. can use as keyword when defining:
+ extern (just does declaring rather than defining too. means memory can be allocated in eg other file
+ typedef

stages:
+ lexer
+ parser (to intermediate form)
+ generator (to assembly)
(does one (or more) of these stages use abstract syntax trees? if so discuss? after section on AST for formulae.

dynamic vs static libraries (??)

programming language semantics
+ operational semantics
+ programming language theory

c code itself stored in memory, before global
\subsection{h3 c structured/procedural}

c:
+ passing arrays to functions. what is passed? reference ot first? length separately?
+ repeating an array n times

auto (local variable, in block scope inc functions). don't need to do, done automatically in local scope

static (global variables. done automatically in global scope, but can do when defining functions)

when declaring a function, eg "int foo(int);", implicity adds extern before. means can declare many times in eg different files, define once

iterating over a string in c
\subsection{h3 natural numbers algorithms}

GCD/LCN algorithms here. Euclidian algorithm?

page on factorial

