
\subsection{Introduction}

APIs in network. REST

mathjax. mathml(mathml upstream elsewhere?)

Deconstructing object. {a, b, c} = myObj;
arrow functions can't use "this"?
.push in array to add to it.

js:
"+" before variable to make it a number
+"5.3" makes 5.3
+ +"0xAA" makes 170
+ uses the valueOf() method in an object, can define for custom stuff too.

webapis (where running async tasks are stored when in browser runtime
+ different name for node?

can use "this" in function, not just object. gets window? what about node?

"export" keyword. used for multiple files
"import" rgddr "from"

static keyword for methods

rename h3 with eg do to "web api"

garbage collection

try catch

timer for code
To see out of date.

\begin{verbatim}
npm outdated
\end{verbatim}

Update minor versions.

\begin{verbatim}
npm update
\end{verbatim}

Update major versions.

\begin{verbatim}
npm install <name>@latest
\end{verbatim}

Audit.

\begin{verbatim}
npm audit
\end{verbatim}

See warnings for existing packages by installing them, either manually for each one, or by:

\begin{verbatim}
rm -rf node_modules/
npm install
\end{verbatim}


\subsection{BASICS}
\subsection{numerical variables}
how dynamic typing works. is it duck typed? implicit conversion?

if use "var", can be hoisted up out of bracket scope

semi colons are optional
use strict
+ no octal numbers
\subsection{control flow}
\subsection{functions}
+ passing arrays to functions. what is passed? reference ot first? length separately?
Use of (...args) when defining a function.
"arguments" is a keyword available in functions.
Immediately Invoked Function Expression (IIFE). Anon function expression which is immediately called.
Map; weakmap
call and apply
stack in js
numbers passed by value
(how are strings passed?)

can you use "const" in parameters?

dynamic so no need for generics

use strict
+ no duplicate parameter names in functions

currying and partial application in JS

js supports closures. data moved to heap (?)
\subsection{strings}
\subsection{arrays}
linked lists in javascript:
+ concatenation
+ slice/filter
+ insert
+ pop
+ traverse
+ map
+ sort
+ reverse
js:
+ repeating an array n times
arrays in javascript:
+ concatenation
+ slice/filter
+ insert
+ pop
+ traverse
+ map
+ sort
+ reverse
\subsection{objects and prototypes}

use strict:
+ no defining properties more than once in objects
  * removes "delete" keyword
  * no escape characters

objects are passed to functions by reference

"class" keyword is syntactic sugar

"new" keyword for object constructor

"bind" keyword in js. bind function to object
\subsection{console object}
js console:
console.warn()
console.error()
console.time()
console.timeEnd()
console.table()
JSON object, inc JSON.stringify
\subsection{PARALLEL AND ASYNC}
\subsection{concurrency and event loop}
settimeout

callback queue

promise on async

task queue

event loop

async keyword when defining function. await keyword

two ways:
+ async
+ promises

multithreading discussion here?
\subsection{SERVER}
nvm to manage multiple versions of node and npm. equiv to eg pyenv
yarn as alt to npm
page on npx
\subsection{CLIENT including firefox and chromium as implementations}
directly updating dom
eg to change text, document.body.x = "hi" (is this right? check?)
do similar for CSS? update the CSS?
+ cookie
+ user agent string
+ fingerprinting
+ cookies
+ user angent string (maybe later? contains info on layout). part of http
window.document.querySelector()
querySelectorAll()
when have, can do addEventListener()
links to js pages in html

can't render unless stack clear? check
dom: scroll event
window.document (window object. document object a parameter of that)
js inline in html

