
\subsection{Introduction}

Burgler alarm. how do they work

	cement ingredient in concrete

	cement: limestone + clay

	concrete: cement + water + sand + rock

	bricks: from clay

	lime: hydraulic lime vs non-hydraulic lime
		hydraulic - harden with water
		non-hydraulic - harden with air
		both breathable, but non-hydraulic slightly more so
		non-hydraulic lime is aslo called putty
			but also available in non-putty form - can have powder

		nhl 3.5 - 3.5MPa (Megapascals)
		refers to strength after 28 days
		exists: 2, 3.5, 5
			higher is stronger but less breathable

bike stuff
700x25. 700 mean mm diameter of tire. standard road size. 25 mm means width of tire. is 25 or 28 generally
road bikes can generally fit either of 25 and 28
valves
+ presta valves. thinner, has nut on top to tighten. more common on road bikes
+ schrader valves. wider, no nut
+ also have dunlop values, but less common

rim brakes vs disc brakes
can use lubricant on chain if rim brakes, not otheriwse

Engineering. Wood screw Vs screw Vs nail


engineering
	making sawhorses
	making handtools

Patch co for ceilings? Has fibres?

Companies for lime:
Chalkdown lime
Mike Wye
The limestuff
Road to jericho

main british rifles
lee enfield
+ .303", 7.7mm (x56mm)
l1a1 self loading rifle (slr)
+ 7.62x51mm ammo (nato)
+ aka FN FAL
SA80 L85A1 bullpup (bullpup means grip ahead of ammo chamber)
+ 5.56mmx45mm (other nato)

usa rifles
m1903 springfield
m1 garand
+ 
m14
+ 7.62 nato
m16
+ 5.56 nato
m4 carbine
+ 5.56 nato


NHL for plaster??
https://cornishlime.co.uk/products/lime-binders/st-astier-nhl/
https://www.lime.org.uk/hydraulic-lime-st-astier.html

easifill brand for polyfiller

Drills. 3 different head types?
Hammer Vs other setting
knife maintenance - honing with rod, sharpening with whetstone
ceramic whetstone vs diamond sharpening stone
steel honing rod or ceramic honing rod
leather strop

Spalling brickwork?
How does soakaway work?
Porous Vs non porous bricks?
Steel lining
Firm flex lining?
flue for chimney
Paint spot repair
Using paper in corners and "plastering" over
Chimney cowl
Chimney flue
Filler Vs caulk? Filler can be sanded, but this not important for skirting boards
For skirting boards can also use filler though? Or adhesive if gaps could go back
Caulk shrinks after use?
Drywall Vs sheetrock
What is drywall mud?
Chimney flaunching?
non-electric clocks

typewriter

non digital photography

Telling north with time and sun
Moss?
North Star Polaris. Other constellations.

ax
saw

cartography
timekeeping
compasses

Bike engineering
Fork shape
Wheels, tyres, inner tube
Brake system
Suspension
Handlebar
Gear chain

food preservation
\subsection{Bushcraft}

Cordage. Eg stinging nettles

Shelter. Y sticks, main stick, bravken?

fibre tarp

making shelters

Tree identification?
Plant identification

\subsection{Water preparation}
water filters
+ Granular acivated carbon (GAC)
+ total dissolved solids (TDS) is metric
+ brita filter is either granular activated carbon or powdered actived carbon AND ion exchange resin (hardness and lead?)
+ other more complicated ones include block carbon or reverse osmosis

Water. Plastic bag on branch

Water prep
Water filtering
Boiling to avoid virus bacteria parasite.
Can still have heavy metals chems
Iodine tabs? chloride tabs
heating water

\subsection{Fire}
food cook
Fire starting? Flint steel etc.
Spark. Tinder bndle

kiln
\subsection{Pottery}
pottery
ceramics
\subsection{Wood}
making charcoal

making fire:
+ prep area (can't spread) with clear grass, surround with stone
+ bow drill?
\subsection{Stone}
stone chipping

Quernstones:
+ for grinding
\subsection{Metal work (bronze, iron}
forges
wrought iron
cast iron
Knife types. Scandi grind? Sharpening knife?

Whetstone? Steel sharpener? DC diamond carbon
Stropping a knife?

\subsection{Animal}
crayfish traps
lobster pot
spear fishing
net fishing
squirrel pole snare
animal tarp

Animal preparation. Gut fish. Bird. Mammal.

+ fur
+ leather
+ wool
Rabbit. Put net over each Warren hole
Put ferret into Warren. Catch rabbit in net.
Can also smoke them out?
Spring trap

\subsection{power generation, piston and gears}
linkages

mechanisms are things which transmit different types of motion

gear systems:
+ standard
  * gear ratios
  * chain drive
  * belt drive
  * ratio of teeth (circumference?) of first and last chain all that matters
  * every gear reverses direction
  * idler gears (ones not first or last)
  * drive shaft is the thing that goes into first (or last?) gear? rotating cylinder
  * external gears vs internal gears. external normal looking ones, but internal possible too
  * spur gear (standard?) vs helical gear
+ changing motion types
  * screw thread: converts from rotation to up/down
  * worm gear: similar to screw? less efficient?
  * bevel gear: eg gears at right angles, so motion changed by 90 degrees
+ time
  * escapement. moves regularly, used in clocks/watches
+ bike
  * freewheel (how bikes work so can move without pedalling)
  * freehub?

gearings:
+ change direction, by being at angle
+ change speed, by relative teeth

watermill: water movement to rotation

windmill: water movement to rotation

external combustion engine (steam engine)

internal combustion engine

piston. rotate to up don. with connecting rod

piston valves
\subsection{home engineering: foundation}

foundations:
+ excavate for foundations
+ fill foundation

underpinning
+ strengthnng existing foundations

\subsection{home engineering: structural stuff}
Wood nail vs drtwoid nail

Building a stud wall

noggins
+ between joists or studs to increase strength

loft trap
+ is the hatch to get in via ladder

staircases

Lintel for construction.
+ goes above where windows/doors/fireplaces go

trenches backfilled with pea shingle

logical flow of construction
+ foundation
+ floors/walls/roof, single story, inc damp proofing
+ multi story
+ insulation of walls/ceiling/floor
+ ventilation of properties, types of ventilation

construction notes
+ damp proof course. phyiscal layer or injection between ground and bricks, floor.

clay (walls etc)

scaffolding

House maintenance: repointing. Reapplying mortar to bricks?

partition walls, load bearing walls, removing load bearing walls with reinforcement?

Prestressed concrwtt
Beam and block
Beam
Frame all as structural engineering
Joists and bearers under floor?
Floorboards
Breathable walls?
Roofs
sawn lathe exists.
Riven before
Riven doesn't give
Sawn does.
Always would give, no big problem?
\subsection{home engineering: drain}
Drains can be on different systems. Rainwater Vs waste water. Rainwater front Vs back. Branching sewer pipes, traps, access ooints
soakaway or something similar sounding for rainwater?

How to unblock drains

drain rods for maintaining and unblocking drains
also boiling water
then bicarb soda and vinegar 50:50 mix for 10mins then more hot water

trenches for drainage runs
Lead flashing
connect sewer to drains

guttering
downpipes
\subsection{home engineering: plastering, lathe walls, paint and distemper}
wall plaster can be modified to be damp proof?

tack ceiling?
+ plaster board over ceiling?

wall plaster
+ wood applied to eg brick, then plaster between, smooth with lathe

Plaster and tanking??

Plaster Vs plasterboard
Lath and plaster for interior walls

1 and 3 putty and
3 lime 2 fine sand is finish

Filler can use polyfiller? Easy to sand.

Chalk and lime Vs
Sand and lime
Lime and chalk more modern. Can do in one go?

Perlite can be base for lime??
Distemper is animal glue lime wash alternative

Types of paint. Silica paint?

Floating coat Vs finishing coat for plaster

Should we have breathable not external walls?

painting walls, removing paint

Distemper/lime wash

Blown plaster on notes. Applies brick and lathe differently?
Mesh plaster for reinforcement

plastering
|                                        | lime | gypsum plaster | gypsum plasterboard | mesh lime | mesh gypsum | cement render | hardwall |
| interior wall lathe new                |      |                |                     |           |             |               |          |
| interior wall lathe repair             |      |                |                     |           |             |               |          |
| exterior wall inside face brick new    |      |                |                     |           |             |               |          |
| exterior wall inside face repair brick |      |                |                     |           |             |               |          |
| interior wall brick new                |      |                |                     |           |             |               |          |
| interior wall brick repair             |      |                |                     |           |             |               |          |
| ceiling lathe new                      |      |                |                     |           |             |               |          |
| ceiling lathe repair                   |      |                |                     |           |             |               |          |

Notes on techniques below
Meshing
gypsum plasterboard
+ aka drywall
+ variants exist like soundproof or insulated

Lime Vs fibre lime
Fibres reduce future cracks?

Fine lime putty, fine lime sand
Lime wash not on ours at least dining room
Animal glue instead

Only external walls need to breathe?

Parting wall not sure if need to breathe?

\subsection{home engineering: doors and windows, ventilation and insulation}
External wall insulation
Other wall insulation?

Draft proofing doors
Draft proofing letterbox
Loft insulation / loft hatch
Cavity wall insulation
Inner wall insulation

loft ventilation

Subfloor ventilation

how to insulate walls, existing walls.
insulate floors, ceilings, existing floors ceilings
ventilation grilles/ventilation strips

Window types. Flush mount

Escutcheon for keys
Windows, double glazing
Window trickle vent

\subsection{home engineering: dectoration}
On decorating, how to sand and wash wall
Sand first?
Can wash with sugar water?

Painting

To make primer mix with water
Emulsion paint: add 10% water
Mix these in the tray

Sanding walls before painting: sandpaper Vs sand block Vs orbital

Step 1 sweep up dirt
Sugar water on floor. Mix water with sugar water with ratio on packet. In bucket.other bucket of clean water. Normal sponge. Wear glvoes
+ Scrubbing with sugar water
+ [Optional: use special scraper to remove any paint]
+ Rub with steel wool 0000
+ Wipe with damp wet cloth
Do this plank by plank. Part of plank.
Use as little liquid as possible
Brush with grain

Step 2 When dried
Decant beeswax turp thing into mini bucket pot
Use 3" brush
Brush along
Easier than cleaning because just one thing
Leave for 6 hours
Can then do second one

Step 3 Buff floor

lining paper for painting on
Mist coat paint is simply watered-down emulsion paint,
Polyvinyl acetate primer, or PVA primer

emulsion paint
	matt paint is type of emulsion paint


painting
+ do ceiling before
+ do prime then 2 layers
+ can make primer from 10% water and rest paint
+ masking tape on things
+ cutting in when painting

Cournicing

Thermal lining for curtains
Sealing gaps and cracks in floorboards

architraves

ceiling tiles

wallpaper

Wallpaper lining goes under wallaper
between skirting board and floor: scotia or quadrant

Skirting boards
\subsection{home engineering: sort}
second fit carpentry:

roof truss
+ framework of timpers to support roof

wallplate
roof binders, roof bracing,

roof dormers
roof: fascia, soffit
roof: undercloaking, verges
roof: felt and batten roof
roof: tiles and slates, ridge/hip tiles, valley tiles, fibreglass/lead tiles
roof: flashings, skirtings
roof: painting/stain fascias, barges

upstands, gullies



carpentry: first fix

floor screed
protective hardcoard/cardboard laid on screed

\subsection{home engineering: electrics}
running electric cables: fish tape; fishing rods, crawl space

carcass wiring
backplates for sockets

how electricity goes across floors, how it goes up floors

electric meter

eleectronics in home. ring circuit vs radial circuit.

fuses, breakers

electric wiring:
+ consumer units
+ bonding?
+ electrical reading on sockets not acceptable?
+ fuse board
+ power over wifi?

\subsection{home engineering: basic water}
how to Remove air from hot water pipes? cold water? just run, or?

Attaching lino / lvt to floor and making waterproof on notes. Inc attaching to bath?

waste pipe sizes, material

to what extent does mains pressure vary? how does going higher affect? how does adding more taps affect?

gate valve?

why have cold water tank vs mains pressure? resiliance to changes in mains pressure/supply
downside: space for storage, pressure is gravity and can be lower, water from cold water tank not potable

material for water pipes, lead, copper, steel.
hard water, soft water

overflow pipes above tank?

pipe tee
direct cylinder?, indirect cylinder

water pipe sizes on main. do they change as get further/split?
water pipe sizes on gravity. do they change as get further/split?
how water pipes are transmitted across floors
migrating from direct to indirect, and visa versa, impact on pipes?

if want to work on pipes, how to remove all water? just turn off input and wait, or something else?

mains water supply

inside stop valve (aka stopcock, aka stop tap). can turn with valve. can replace with SureStop, changes with switch instead.
can also add aladdin valves on live hot or water pipes to make them valves
can do freezing and clamping as short term solutions

toilets

outside stop valve (responsiblity of water company)

water systems and drainage systems
rising main: thing which takes water to up each floor

water systems: indirect vs direct.
+ indirect: water splits and goes to drinking water (usually on ground floor) and cistern in roof. cold water tank.
+ direct: water goes direct to each thing

dishwasher (generally take in cold water, water out)
washing machine (generally takes in cold water and heats up itself, water out)
dryer (no water in, but water out)

adjusting taps if gravity vs mains pressure

home mainenance:
ceramic stuff: bleach; limescale remover

blocked pipes

water meter
\subsection{home engineering: gas for hot water/heating}
Deck mounted taps Vs wall mounted taps
Thermostatic mixer

vent pipes

underfloor heating (UTH)

flue can't be next to door, window, gutter

Fire place, hearth, flue, hearth stone?
Fireplaces on multiple floors
Blocking fireplaces from animals, rain?


system boilers use unvented hot water cylinder

vented hot water cylinder vs unvented

if cold water storage tank, that feeds into boiler

with cold water storage tank, cold water from there, and hot water, is not potable
means that for any sink which uses mains water, eg kitchen, can't have mixer

what sort of boilers require condenser output, require flue output, where does each need to go t



boiler return pipe
dipped return

two port and three port valves to control temperature and heat flow

pumped heating and gravity circulation vs fully pumped system. (cold water falls by gravity, hot water rises)

capping off gas

gas fire

immersion heater

gravity rad?? what is

if working on hot water/gas, how to ensure pipes are empty? turn off mains and then?

electric boiler



sink unit

bath/shower




showers
+ electric shower. takes in cold water, heats it up using electricity. no need for hot water input/boiler. weak water flow?
+ mixer shower. mixes hot and cold water. requires boiler. can have stronger water flow. does not need electricity
+ power shower. requires hot and cold water. requires boiler. requires electricity

gas in; flue out? condenser out?
gas meter

boiler types:
+ electric boiler
+ gas boiler
+ gas condensation boiler
+ heat pump boiler
table of how they vary: requirement of cold water tank (none?) requirement of hot water tank, output pressure, what waste is (flue/vent stuff for gas related) (most of these criteria aren't boiler specific maybe?? eg can have gas using gravity or combi)

airing cupboards

how hot water pressure is affected by boiler types
+ hot water in other stuff (inc adjusting eg showers if gravity vs mains pressure, and power showers)

what's difference in capacity between combi boiler and condenser boiler and system boiler?

+ conventional boiler: heats a hot water cylinder. water taken from hot water cylendar as needed. also heats radiator pipes, but these are on a separate circuit
+ combi boiler: heats water on demand, no hot water cylinder or cold water tank. if more demanded than can produce, no storage to go back on. single circuit for hot water and heating, which means one heating thing which swaps between heating radiator circuit and water for use in eg shower
+ heat pumps / electric boilers can replace gas in both cases

then thing on different styles types
+ system boiler
+ combi boiler
+ back boiler
+ traditional boiler

single vs double radiators. twice as much capacity?
radiators
powerflush
+ reflectors make them more efficient. can install between radiator and wall
+ radiator water is in closed circuit. if air is trapped in system, can bleed radiator to free space. water can be added to increase pressure
+ radiators have a circulating pump to make the water circulate around. electrically powered
+ underfloor heating can use circuits like radiator circuit, but can also use heat pump stuff?


