
\subsection{Introduction}

swaps for finance. Can we back out projection of paths from it?
various payment systems

FedNow
FedACH
Single European Payment Area (SEPA)
LINK
Fedwire
Clearing House Interbank Payments System


liability driven investment strategy


regulation
+ ramsey problem for thinking about pricing

point is costs to identifying who to lend to. banks can do that better. also transaction/scale costs for large lending, enforcement.

also, people want short term svings, borrowers want long term. page on reserves. page on full reserve banking, page on fractional reserve banking, bank failure

benchmark and index providers
market data vendors

Proprietary trading

Index funds: arbitrage during rebalancing
\subsection{Big h3: International economics}
\subsubsection{Trade}
\subsubsection{Gravity model of international trade h3}

\subsubsection{Ricardo model h3}

\subsubsection{Heckscher-Ohlin model h3}

\subsubsection{Hecksher-Ohlin theorem}

\subsubsection{Rybczynski theorem}

\subsubsection{Stolper-Samuelson theorem}

\subsubsection{Factor-price equalisation theorem}

\subsubsection{Marshall-Lerner condition}

\subsubsection{H3 on New trade theory}

\subsubsection{Big page: International economics}
\subsection{bank as matching deposits to lending}
\subsection{payments and payment services}

payment systems in banking:
+ bank notes as currency
+ making payments within the same
+ making payments to other banks
+ making payments ot banks with other base currencies

payment (cash, interbank (push/pull, reversibility, capital requirements),card systems ,
(interchange)

split out payments
+ payment in base currency (eg gold)
+ payment in bank notes (eg coins)
+ push bank-to-bank transfer (eg fps)
+ pull bank-to-bank transfer (eg dd)
+ card systems
+ international payments (eg swift)

\subsection{central banks}
deposit insurance in central banking

\subsection{investor advisors}
\subsection{credit rating agencies}
\subsection{fund managers (active and passive investment)}
trend following strategies? worth mentioning?
\subsection{exchanges}
Market makers

trade data
+ pre
+ post

exchanges:
+ fee structures
+ pay for crossing gap. useful in single exchange
+ execution
+ order books. whole amount willing to buy or sell at different prices

multi exchanges
+ open exchange vs ?
+ cross exchange arbitrage, competition

role of darkpools?

\subsection{trading inc HFT}

