
\subsection{Introduction}

Clusters of Linux machines on networks. Beowolf cluster

traeffik
	alt to nginx?


git stuff:
+ git config --get pull.rebase
+ git config --global --get pull.rebase
to find out if default is rebase
networks: network address translation (NAT)

linux: nmcli network manager cli, also nmtui (text user interface)

previous known as letsencrypt/lets encrypt


Install certbot

\begin{verbatim}
https://certbot.eff.org/instructions?ws=apache&os=ubuntufocal
\end{verbatim}

\begin{verbatim}
sudo certbot --apache -d bou.lt -d www.bou.lt -d cloud.bou.lt
sudo certbot --apache -d economoose.com -d www.economoose.com
sudo certbot --apache -d artificialeconomist.com -d www.artificialeconomist.com
sudo certbot --apache -d yetipredict.com -d www.yetipredict.com
\end{verbatim}

Might not be necessary by default, auto does?
\begin{verbatim}
sudo certbot renew
\end{verbatim}

nfs on networks if it isn't there already? sshfs (might be better if only sometimes available). page on samba too.
networks: nfs:
+ showmount -e server\_name (part of nfs-utils)
+ showmount -e tower
+ mount -t nfs server\_name:/path/to/dir /mnt/nfs
+ mount -t nfs tower:/media/adam/Five-0/Media /mnt/nfs
+ umount -f -l /mnt/nfs


git log @{u}..
checks for unpushed commits. in my script use that and only push if not nothing.

tor
maybe thing in networks on c server?
+ Algorithmic complexity attack (make software use worst case complexity rather than average case?)

view git commits since last push:
+ git log origin/master..HEAD
view diffs since last push:
+ git diff origin/master..HEAD
merge unpushed commits:
+ git rebase -i origin/master


/etc/hosts.allow and /etc/hosts.deny are legacy and from tcp\_wrappers.

systemd-resolved. alt to dnsmasq?? or is it??? something about stub?
Name Service Caching Daemon (nscd)


blocking known DoH providers by domain in dnsmasq, and by ipaddress in iptables


/etc/resolv.conf
nameserver 127.0.0.1

sudo systemctl restart dnsmasq

mac address and mac address spoofing. reverse - getting information from mac addresses. cloned mac addresses
development stuff:
+ continuous integration (CI)
+ continuous delivery/deployment (CD)

vpn
tor

tailscale

CDNs (content delivery network), or should this be elsewhere?
APIs
DDoS

sequoia: pgp library.

network: sharing drive using samba. nfs as alternative

on networks, page on syncing (eg rsync, syncthing) and another page on backups (eg borg? backburner?)

timeshift on network (section on offsite backups more generally?)

role of things like cloudflare in networks? or elsewhere?

/etc/ssh/sshd\_config
can use this to prevent ssh login as root

rfkill. used for disabling network devices at kernel level

viruses: and worms? concept of spread and replication not in trojan (which are discussed in unix)

+ Pretty Good Privacy (pgp). proprietary software. collection of existing algorithms, not algorithm itself so belongs in unix/networks
+ openpgp. open source implementation
+ gpg (gnu privacy guard). another open source implementation

tcp over tcp tunnel a bad idea because tcp relies on loss? check?

sshuttle

torrent on network

ipfs on network?

denial of service:
+ ddos
+ regular expression denial of service (ReDoS)

remote procedure call

page on buildbot?

openssh in name for ssh. (also sftp, scp, ssh-add, ssh-agent, ssh-copy-id, ssh-keygen, ssh-keyscan, sshd)

iptables and iptables-nft. before ufw? or same page? different pacakges though.

/etc/resolv.conf for dns nameserver
can ask router for wide ip address
upnpc -s
\subsection{file transfer protocl (ftp) (outdated, sftp exists, but maybe nfs more relevant?)}
\subsection{secure shell (ssh)}
\subsection{H3: DNS}
Name Service Switch (nss)



/etc/hostname
(dns) ttl. time to live. tells people contacting you how long they should cache for. what happens if you update during cache? can shorten ttl while making changes
dynamic host configuration protocol (dhcp). assiigns ip addresses?
extension mechanisms for dns (edns)
root name servers on dns
dns uses port 53. port 53 hijacking exists as risk. can use dns over https, or dns over tls? dnssec?
dns records: "a record", mxrecord
mx records can be hijacked, as can others?
dig: domain information groper. is command to get ip from dns.
dhcp allocate ip addresses
rfc and codes?related to dhcp?
Dynamic Host Configuration Protocol (DHCP)
how to view dnscache in linux? where stored?
+ not by default on linux
+ but possible under systemd systemd-resolved

dnsmasq. dhcp and dns server?
\subsection{H3: APPLICATIONS}
\subsection{wget and curl}
using curl to go via proxy tunnel
\subsection{apache and nginx}
apache:
+ a2ensite
+ a2enmod
+ rewriting
+ redirecting
+ .htaccess
\subsection{H3: NETWORK MONITORING APPLICATIONS}
network stuff:
+ tcpflow
+ ntopng
+ tshark
\subsection{ntop}
ntop
+ ntopng is next generation of ntop
+ is a daemon. can access with localhost:3000
\subsection{iftop}
iftop (shows activity by domain destination (but often incorrect/not helpful, ie youtube not shown as youtube)
\subsection{wireshark}

wireshark
+ gui. similar to tcpdump

\subsection{nethogs}
nethogs
+ shows activity by process. can find out what processes using bandwidth
+ tcp only? doesn't show udp traffic
+ newer versions allow udp too. -C flag
\subsection{H3: SETTING UP OTHER MACHINES}
on networks, h3 on setting up other machine:
page on ssh-copy-id (from openssh, so indicate in chapter name, and have earlier page on rest of openssh)
note can disable remote password logins:sudo nano /etc/ssh/sshd\_config
ansible:ansible-playbook --connection=local 127.0.0.1 playbook.yml
same rsa key pair can be used for openssl and openpgp/gnupg. discuss in networks. page on openssl, openpgp, gnupg
\subsection{H3: OTHER APPLICATIONS}
security
+ sqlmap (find vuls in online applications)
+ metasploit
+ burp suite
+ OWASP ZAP
\subsection{aircrack}
Aircrack-ng. crack WEP keys on wifi


