
\subsection{Definition}

A sequence is an ordered list of terms.

These are commonly maps from natural numbers to real (or complex) numbers.

We can use \(a_i=f(i)\) to denote this.

If \(f(i)\) is defined on all \(i\in \mathbb{N}\) then the sequence is infinite. Otherwise it is finite.

If a sequence is defined on \(n\in \mathbb{N}\) and \(n\ne 0\) then the sequence must be defined on \(n-1\).

For example \(a_0, a_1, a_2,...\) is a sequence, but \(a_1,a_2,...\) is not.

\subsection{Monotone sequence}

A monotone sequence is one where each element is succeeded ordinally by the next entry.

For example:

\(<1,2,3,6,7>\) is monotone

\(<1,2,3,3,4>\) is not monotone

An increasing sequence is one where:

\(\forall m \in \mathbb{N} \forall n\in \mathbb{N} [m > n \leftrightarrow a_m \ge a_n]\)

A strictly increasing sequence is one where:

\(\forall m \in \mathbb{N} \forall n\in \mathbb{N} [m > n \leftrightarrow a_m > a_n]\)

A decreasing sequence is one where:

\(\forall m \in \mathbb{N} \forall n\in \mathbb{N} [m > n \leftrightarrow a_m \le a_n]\)

A strictly decreasing sequence is one where:

\(\forall m \in \mathbb{N} \forall n\in \mathbb{N} [m > n \leftrightarrow a_m < a_n]\)

All strictly decreasing sequences are decreasing, and all strictly increasing sequences are increasing.

A monotone sequence is one which is either increasing or decreasing.

\subsection{Subsequences}

A subsequence of a sequence is the original sequence with some elements of the original removed, not changing the order.

For example:

\(<1,3,5>\) is a subsequence of \(<2,1,3,4,7,5>\)

