
\subsection{Introduction}

R packages are generally installed from source

r has named vectors. Like dicts???

r: renv for package management. rig for pyenv equivalent.

shift equivalent on R. ie take lagged variables

r:
+ repeating an array n times


S3 vs S4 vs RC vs R6.

sloop package (Relates to OOP)
otype(obj) return object type. more granular than is.object()
objects are base objects or oo objects
class()
typeof()

linked lists/arrays in R
+ concatenation
+ slice/filter
+ insert
+ pop
+ traverse
+ map
+ sort
+ reverse

methods are outside of variables. eg f(x) rather than x.f()
is this generics?
eg can do names(list) names(df)

macro nature of R. eg can do %>%. bit like lisp

iterating over a string

how dynamic typing works. is it duck typed? implicit conversion?

parallel h3
functional h3

library: obj F\_addr, lobstr

r startup:
+ look for .Renviron
+ look for .Rprofile
+ look in the following order. first match used
  * current dir (getwd())
  * HOME (Sys.getenv("HOME"))
  * R\_HOME (can check with R.home())

base package:
+ eval
+ names
+ diff
+ table
+ do.call
+ try (to see if error, catch it)
+ apply
+ tapply
+ length
+ tracemem
+ cut
+ stopifnot (R version of assert)

base but for dataframes
+ colMeans
+ by
+ rowSums, colSums, .rowSums, .colSums


stats package (Default)
+ aggregate
+ xtabs

r stop script from anywhere without throwing? quit?

R:
+ copying in R
+ timer for code

data structures, and accessing parts using [i,j], [i], [[]], \$
+ data creation using csv, through explicity series and lists

\subsection{BASE}
\subsection{basic terminal input and output}
+ logging
+ readline

\subsection{classes in R}
class() function exists
\subsection{DATAFRAMES}
\subsection{REGRESSION ETC?}
\subsection{standard stats}
filter is stats r package

base r(in stats package?): ave

base r(stats pacakge): setNames

rnorm(stats) function
runif(stats) function
\subsection{formula stuff}
+ formula writing: y ~ x + m. or a*b interactions. a:b interactions
+ training models OLS
\subsection{CONT}
\subsection{working with os}
r os stuff:
+ getwd
+ setwd

+ IO in base. read.table etc read.csv etc are variations on read.csv
\subsection{integrating with bash}
+ grab arguments from bash?
\subsection{multi threading}
\subsection{interactive interpreter}
R "?" Command for manual
clear for R
\subsection{PACKAGES}
\subsection{how to use libraries}
renv replaced packrat

+ namespaces in R
require vs library

library
require
\subsection{creating libraries using R}
\subsection{creating libraries using [c?]}
\subsection{r tidyverse}
map

rlang:
+ package. part of tidyverse
+ !!, !!!, as\_name, sym

magrittr (pipe %>%)

plyr vs dplyr
bang bang "!!" in dplyr
+ mutate/select/filter/summarise/arrange
+ group\_by\_ungroup()
\subsection{rstudio}

rmd
knit
kable
+ rmd in R
"vignettes"

+ View()
+ view() (lowercase, in tidyverse maybe?)


