
\subsection{Introduction}

tobin's q here or elsewhere?
+ market value / replacement value
+ (equity market value + liabilities market value) / (equity book value + equity book value)
+ can do for whole economy: stock market value / corporate net worth

market to book ratio
+ equity market value / equity book value

book to market ratio
+ equity book value / equity market value


Free cash flow

\subsection{General ledger}
- Costing
\subsection{h3 on single entry book keeping}

+ cash
+ accounts receivable
+ accounts payable
+ taxes
+ page on depreciation and amortisation
+ can compile into income statement. basically a summry of the book over a certain range
+ sum by credit or debit. by type of income/outgoing
+ divided into sections (revenue/expenses[cost of goods sold, selling general admin aka SGA, depreciation amortisation, r\&d])
+ non operating section (other revenue or gains eg rent; other expenses or losses eg forex, finance costs eg interest, tax

something on accrual based accounting

working capital. capital asset. current liability

ebit
ebitda
ebita

different methods. generally accepted account practices (GAAP); international financial reporting standards (IFRS)

\subsection{balance sheet}
from general ledger
\subsection{cash flow statement}
something on cash flow statement. income statement but without things like accruals. maybe cash flow statement is before?
from ledger
\subsection{income sheet}
from general ledger
\subsection{statement of changes in equity}
\subsection{double entry book keeping}

