
\subsection{Introduction}

transpilers,
+ llvm can do this, so can discuss c++ -> C. c++ -> IR -> C

cpp uses libstdc++, equiv of glibc

C++:
frame as bare metal and hosted c++, and stdlibc++ or whatever it is called.

is there a concept of freestanding C++?
+ manually write eg new, delete, what other functions?
+ yes hosted c++ and freestanding c++ exist as concepts, but linux kernel just written in c, not c++, so leave?

late binding a thing which c++ does which c doesn't? "virtual". can have some objects which are not known at compile time?

c++:
+ passing arrays to functions. what is passed? reference ot first? length separately?
+ repeating an array n times

later on c++, different c++ standard library implementations. are various.

big thing on closures in c++? nested functions. are located on the heap not the stack? check?

new array and linked list type things
+ concatenation
+ slice/filter
+ insert
+ pop
+ traverse
+ map
+ sort
+ reverse

new keywods:
+ virtual
+ noexcept
+ override
+ const after function declaration

getters and setters

page on memory allocation on heap in c++, after c standard library

iterating over a string

operator overloading

changes to c standard library: printing
"this" keyword in structs, classes (in methods)

algorithm header file (standard c++ library?) has for\_each function. functional related?

h3 on functional programming
currying
std::transform. can do simple functional?
functors
lambda
std::bind (partial function application)

partial functions in h3 section on functional

something on polymorphism (can be done in the context of structs)

parallel threads
\begin{verbatim}

#include<thread> // std::thread

void foo();
void bar(int x);

// Carries on after starting thread
std::thread first (foo)
std::thread second (bar, 0)

// Following waits for threads to finish
first.join();
second.join();
\end{verbatim}

\subsection{OBJECTS and CLASSES}
\subsection{reframing c structs as objects}
structs still exist, but objects can be used instead
\subsection{new things in objects, inc inheritance and OOP (h3?)}
dynamic name binding on derived objects?

encapsulation?

how methods talk to each other. encapsulation

class templates
operator overloading. eg can make "+" do something for custom class



public methods and private methods
\subsection{inheritance}
creating inherited class c++, inherit from multiple?

messages are sent betweeen objects. via inheritance?
\subsection{object oriented programming}
motivation behind OOP. global state leads to problems. answers are objects oriented or functional.
\subsection{PACKAGES}
\subsection{standard library: stuff from c and changes}
h3 on standard library. page on use of c standard library. page speciifcally on malloc to new. on << and >>?
\subsection{standard library? new pointer things}
Shared pointer
Unique pointer
weak pointers
smart points

smart pointers do reference counting. do any others?

\subsection{other new stuff in standard library}

vector as data type
+ part of c++ standard library, not in regular c


