
\subsection{Introduction}
 
.emacs file; changing screens; opening files; search; saving

\subsection{Saving and exiting}

exit:
\begin{verbatim}
C-x C-c
\end{verbatim}
Save:
\begin{verbatim}
C-x C-s
\end{verbatim}


\subsection{GUI only: Font size and zooming}

zoom out
\begin{verbatim}
C--
\end{verbatim}
zoom in
\begin{verbatim}
C-+
\end{verbatim}



\subsection{Searching}

search forward:
\begin{verbatim}
C-s
\end{verbatim}

search back:
\begin{verbatim}
C-r
\end{verbatim}


\subsection{Copy and paste}
emacs copy paste


\subsection{Undo and redo}

\subsection{Buffers and reading other files}

read file:
\begin{verbatim}
C-x C-f
\end{verbatim}


switch buffer:
\begin{verbatim}
C-x b
\end{verbatim}

kill buffer
\begin{verbatim}
C-x k
\end{verbatim}

emacs mode buffer. has info on file and mode



\subsection{Need to install: Magit-mode}

For git

\subsection{Company-mode}
COMPlete ANY

\subsection{dired}
File browser. Installed by default.

\subsection{Need to install: Evil mode}

Use vi style bindings.

\subsection{Javascript}

\subsection{Shell}

Start a shell:

\begin{verbatim}
M-x shell
\end{verbatim}

\subsection{Customising}


\begin{verbatim}
~/.emacs
~/.emacs.el
~/.emacs.d/init.el
\end{verbatim}
  
\subsection{eww (Emacs Web Wowser)}

Installed by default.

\subsection{Macros}
Allows you to see value of variable set:

\begin{verbatim}
M-x describe-variable
\end{verbatim}


M-x concept. runs macros?
C-sfsjfls is shortcuts for macros? so for each thing should have the M-x and C-ses equivalent?



\subsection{Windows}

close window:
\begin{verbatim}
C-x 0
\end{verbatim}
close other windows:
\begin{verbatim}
C-x 1
\end{verbatim}
split on x axis:
\begin{verbatim}
C-x 2
\end{verbatim}
split on y axis:
\begin{verbatim}
C-x 3
\end{verbatim}
switch windows:
\begin{verbatim}
C-x o
\end{verbatim}
Make window wider:
\begin{verbatim}
C-x }
\end{verbatim}
Make window thinner:
\begin{verbatim}
C-x {
\end{verbatim}
balance window size:
\begin{verbatim}
C-x +
\end{verbatim}
make window smaller:
\begin{verbatim}
C-x -
\end{verbatim}

\subsection{GUI vs terminal}

to start in terminal mode:
\begin{verbatim}
emacs -nw 
\end{verbatim}

\subsection{Package maangement and MELPA and ELPA repositories}

\begin{verbatim}
M-x list-packages
\end{verbatim}

i/I
d/D
x to execute the activity

\subsection{Tramp for remote access}

Built into Emacs

\subsection{Python mode}

to get python interactive shell from within python mode

\begin{verbatim}
C-c C-p
\end{verbatim}

"run-python" macro

python.el provides python mode. built into emacs

elpy (to evaluate script):
\begin{verbatim}
C-c C-c
\end{verbatim}

jedi for autocompletion


\subsection{Org mode}

customising using conf.org file



org mode
use of *
use of +
use of TODO: set with:

\begin{verbatim}
C-c C-t
\end{verbatim}
see agenda
files to be in agenda stored in org-agenda-files

to change state and record note:
\begin{verbatim}
C-u C-c C-t
\end{verbatim}

cycle through agenda files:
\begin{verbatim}
C-'
\end{verbatim}

add current file to agenda files:
\begin{verbatim}
C-c [ 
\end{verbatim}

remove:
\begin{verbatim}
C-c ]
\end{verbatim}

view agenda:
\begin{verbatim}
M-x org-agenda
\end{verbatim}

change theme:
\begin{verbatim}
M-x load-theme
\end{verbatim}


