
\subsection{Introduction}

chef, puppet and ansible as cloud tools

glacier deep archive, like glacier, is s3 compatible?

distributed notes
	h3 on distributed data
		storing data in a distribted way
			Hadoop Distributed File System (HDFS):
			Apache Cassandra

		accessing data stored in a distributed way
			Hadoop
			spark
		apache kafka?

kubernetes: how to use GPUs, CUDA

microk8s ctr image import myimage.tar (can do from docker export?)

kubectl. kubectl apply on yaml files
kubectl create deployment
kubectl scale deployment
kubectl expose deployment

for distributed:
+ rancher
+ docker swarm

Apache kafka (messaging thing?)
terraform on cloud computing.

distributed datasets: hadoop distribed file system (HDFS), Apache HBase, Apache Cassandra (all based on bigtable?)

mapreduce (and apache hadoop, an implementation)
apache spark (builds off mapreduce, better?)

CAP theorem: only 2 of 3: consistency, availablility, partition tolerance.
\subsection{google cloud h3}
\subsection{Microsoft h3}
microsfot snowflake
\subsection{Amazon}
ec2 stuff
+ Amazon Machine Images (AMI)
+ Storage
  * instance storage
  * simple storage service (s3)
    1. object storage. non-filesystem
  * elastic file system (efs)
    1. designed to be used with multiple ec2 instances
  * elastic block store (ebs)
    1. can have snapshot backups
    2. paired with ec2 instances
    3. designed for one instance, but can now be used by multiple?
    4. options:
       1) Cold HDD (sc1)
Aws: patr on elastiv compute cloud (ec2)
Elastic beanstalk meta load balancer and instances
Lambda. Functions as a service
Athena page?
Simple storage service (S3)
Elastic block store
Ec2 instance store
Glacier
Elastic file system
Databases: simple db; Dynamo dB; document dB; rds
Data warehouses: redshift
Data lakes page
Page on graph database in amazon
Elastic search
Amazon glue
Amazon aurora
Machine learning: sagemaker; rekognition; lex;
Tools: IAM
aws:
+ page on elastic compute cloud (ec2)
+ page on load balancers (beanstalk)
aws
+ aws ec2
+ aws ec2 describe-instances
+ aws s3
+ aws s3 ls s3://mybucket
amazon ec2:
+ Identity and Access Management (IAM)

