
\subsection{Introduction}

Gleason's theorem
	can be used to derive born rule?

can we Model discrete physics as moving between eigenstates with unitary operators?

quantum mechanics now describes state as v, and then also Psi as state, and then defines Psi.v seems inconsistent?

physics
	big page: explicitly say qed, electroweak, quantum chromodynamics

	quantum mechanics
		before qed
		non relativistic
		particles have wave like properties
		deriving born rule from many worlds
	qed
		virtual particles
		particles are excitation of underlying field
		renormalisation
		charge symmetry
		parity symmetry
		time symmetry
		chirality and helicity
		muon: electron but higher mass
		tau: higher mass again

		neutrios:
			neutino (electron)
			muon neutrino (muon)
			tau neutrino (tau)
		why these number of electric particles? Unclear
		why only 3? Unclear
		why only -1,0,1. (reasons exist but complex?)
		parity symmetry exists
		energy density of empty space?
	fermion: half integer spin
	lepton: fermion without color

	electroweak
		spontaneous symmetry breaking
		superconductivity? Related to breaking U(1), not sure if part of electroweak, or QED, or requires atoms therefore QCD?
		no parity symmetry. Gives way to define handedness of universe?
		charge symmetry?
		cp symmetry
		cp violations happens for some electroweak phenomena?
		cpt symmetry
		adds new gauge bosons. Qed just has photons
		W\^+, W\^-, Z\^0 gauge bosons
			have mass, unlike photon
			mediate weak force
		higgs boson and higgs field
			doesn't predict why specific masses we see of particles though
	strong
		no cp violations? Unclear why, note there are for electroweak
	page on reconsiling quantum with general
		vacuum catastrophe
		singularities
		hawking radiation

Quantum systems
Set of possible values
Use these as eigenvalues and construct hermitian matrix
State is vector. Vector being equal to eigen vector means at eigen state. Orthogonal states because only 1 at a time
Do that on classical discrete before moving to quantum

quantum
spin statistics theorem
bose-einstein statistics (integer spin)
fermi-dirac statistics (half integer spin)

concept of spin comes from quantum electromagnetism. spinning large object generates field in direction. so does electron

Quantum mechanics
If discrete states sum of states, if continuous integral and coefficient is wave function

nuclear physics
+ nuclear binding energy
+ radioactive decay
+ exponential decay
+ half life
+ fusion
+ fission
+ fissile isotope. most common is 235U
+ enrichment. making ore into 235U from mix of that and 238U
+ critial mass decreses with more purity
+ control rods: absorb material
+ prompt critical neutrons vs delayed critical neutrons
+ effective neutron multiplication factor

number of pure states is the dimension of state vector. if there are 2 states, represent as 2 vector with 0 and 11.

for pauli matrices. start with one, then construct others such that prob = 0.5. so 2 state system results in 3 vector measurements. 3 dimensions

de broglie wavelength

link between hermit matrix and eigen vec val real?

\subsection{quantum computing (h3 for computers)}


on quantum computing: quantum fourier transform. quantum equivalent of discrete fourier transform. exponentially faster than discrete.
quantum error correction in quantum computing.
Quantum: Grover algorithm

quantum computers
+ shor's algorithm
+ postBQP (BQP with post selection)
+ bounded-error polynomial time (BQP) (1/3 cut off)
+ Quantum Merlin Arthur (QMA) verify on quantum computer in poly time



quantum computing
+ turing machines can do all things quantum can do
+ but possibly different complexity classes
+ qubits


page on quantum computing?
+ classical memory: series of bits
+ quantum memory: superposition of classical bits
+ what do we do with these states? in classical apply logical gates. now, apply quantum logic gates
+ measuring state: in classical, simple, deterministic. in quantum, not. want high probability of correct answer
+ types of quantum gates: in classical, can create any using and, not, etc. what is equivalent for quantum?
+ measurement happens at end. otherwise interupts



